---
title: 'R Package “regrrr”: Compiling and Visualizing Regression Results'
author: ''
date: '2019-03-10'
slug: regrrr-one-stop-r-toolkit-for-compiling-regression-results
categories: []
tags:
  - regression
  - R
---

This is an R package <a href="https://CRAN.R-project.org/package=regrrr" target="_blank"> "regrrr"</a> on <a href="https://cran.r-project.org" target="_blank">Cran</a> I coauthored with Rui Yang.

In strategy/management research, we always need to compile the regression results into the publishable format and sometimes plot the moderating effects. This package does the job. 

Here is the quickstart guide.

[![Rdoc](http://www.rdocumentation.org/badges/version/regrrr)](http://www.rdocumentation.org/packages/regrrr)
[![](https://cranlogs.r-pkg.org/badges/regrrr)](https://cran.r-project.org/package=regrrr)

# Installation
To install from CRAN:
```
install.packages("regrrr")
library(regrrr)
```
You can also use devtools to install the latest development version:
```
devtools::install_github("raykyang/regrrr")
library(regrrr)
```

# Examples 
## compile the correlation table
```{r}
library(regrrr)
data(mtcars)
m0 <- lm(mpg ~ vs + carb + hp + wt, data = mtcars)
m1 <- update(m0, . ~ . + wt * hp)
m2 <- update(m1, . ~ . + wt * vs)
cor.table(data = m2$model)
```
## compile the regression table
```{r}
regression_table <- rbind(
combine_long_tab(to_long_tab(summary(m0)$coef),
                 to_long_tab(summary(m1)$coef),
                 to_long_tab(summary(m2)$coef)),
compare_models(m0, m1, m2))
rownames(regression_table) <- NULL
print(regression_table)
```
## plot the moderating effect
```{r}
plot_effect(reg.coef = summary(m2)$coefficients, data = mtcars, model = m2,
            x_var.name = "wt", y_var.name = "mpg", moderator.name = "hp",
            confidence_interval = TRUE,  CI_Ribbon = FALSE, 
            xlab = "Weight", ylab = "MPG", moderator.lab = "Horsepower") +
ggplot2::theme(text=ggplot2::element_text(family="Times New Roman", size = 16))
```

As you can see from the last line of code, the plot is customizable using <a href="https://CRAN.R-project.org/package=ggplot2" target="_blank">"ggplot2"</a>. There are a couple of other functions. Please see the <a href="https://www.rdocumentation.org/packages/regrrr" target="_blank">reference manual on R documentation</a> for details.


